Deep Learning

### 2015-01-22 deepreview.tex
fixed more bib problems
typo

Deep neural networks that learn to represent data in multiple layers
of increasing abstration have dramatically improved the
state-of-the-art for speech recognition, object recognition, object
detection, predicting the activity of drug molecules, and many other
tasks. Deep learning discovers intricate structure in large datasets
by using the backpropagation algorithm to compute error-derivatives
for the weights that define each layer of feature detector and then
repeatedly changing these weights in proportion to their derivatives
averaged over small batches of training examples.  Deep recurrent
neural networks, in which each layer also receives input from its own
state at the previous time-step, can now generate good captions for
images and are competitive for language translation.

@@

\vspace{-0.12cm}
\subsection*{Convolutional Networks}
\vspace{-0.12cm}

>>>>

Deep neural networks that learn to represent data in multiple layers
of increasing abstraction have dramatically improved the
state-of-the-art for speech recognition, object recognition, object
detection, predicting the activity of drug molecules, and many other
tasks. Deep learning discovers intricate structure in large datasets
by using the backpropagation algorithm to compute error-derivatives
for the weights that define each layer of feature detector and then
repeatedly changing these weights in proportion to their derivatives
averaged over small batches of training examples.  Deep recurrent
neural networks, in which each layer also receives input from its own
state at the previous time-step, can now generate good captions for
images and are competitive for language translation.

@@
